---
title: "ASSESSMENT 3- BIOINFORMATICS"
author: "Anushree Desai"
output: html_document
theme: cosmo
---

## Answer 1: The first answer makes use of commands download.file to download a file, and then to read a tsv file I have used read.table command. In order to format the data set we have put header= 'TRUE' and to obtain gene accession names as row.names I have used the command row.names=1. In the end to obtain just the first six rows head command is used. Structure command is used to observe the structure of the data set. 

```{r,chunk1,echo=TRUE}
# Downloaded the data of gene expression file
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/gene_expression.tsv",
              destfile = "assessment3.tsv")
# Reading the table and making sure that gene accession names are the row names
originaldata <- read.table("assessment3.tsv")
originaldata <- read.table("assessment3.tsv", header= TRUE, stringsAsFactors= FALSE, row.names=1) 
# Data imported properly and printing first six rows and structure as well.
head(originaldata)
str(originaldata)
```

## ANSWER 2: We are asked to make a new column with the mean of other columns. First of all, I have used the rowMeans command to find the means of all rows. Then in order to make a new column, I made a new variable and named it as Meansofothercolumn and stored the means into it. Then with the cbind command i attached the new column to the original dataset and made it a permanent change. And in the end with the head command I printed the result of the first six genes.

```{r,chunk2,echo=TRUE}
# Command rowmeans is used to find the means of other columns
rowMeans(originaldata)
# A new column is made with the name of Meansofothercolumn to store these means
Meansofothercolumn <- rowMeans(originaldata)
# This column is bind to the main data now
cbind(originaldata, Meansofothercolumn)
# Permanent change to data. Adding the new column of means
originaldata <- cbind(originaldata, Meansofothercolumn)
# Observe the first six genes to check if new column is added
head(originaldata)
```
